% M. Saqib Arfeen — CV
% Compile with pdflatex. Works out of the box on Overleaf (overleaf.com):
% New Project -> Upload -> this file -> Recompile.
\documentclass[10pt,a4paper]{article}

\usepackage[margin=1.4cm,top=1.2cm,bottom=1.1cm]{geometry}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[none]{hyphenat}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}

\definecolor{rulegrey}{HTML}{BBBBBB}
\definecolor{datedim}{HTML}{555555}

\pagestyle{empty}
\setlength{\parindent}{0pt}

% ---------- layout commands ----------
\newlength{\labelw}\setlength{\labelw}{3.4cm}
\newlength{\bodyw}\setlength{\bodyw}{\dimexpr\textwidth-\labelw-0.3cm\relax}

% \cvsection{Label}{content}
% small-caps section labels like "PROFESSIONAL EXPERIENCE":
\newcommand{\cvsection}[2]{%
  {\color{rulegrey}\hrule height 0.5pt}\vspace{4pt}%
  \begin{minipage}[t]{\labelw}\textsc{#1}\end{minipage}%   % \textbf -> \textsc
  \hfill
  \begin{minipage}[t]{\bodyw}#2\end{minipage}%
  \vspace{8pt}\par
}

% bold + underlined company names like his:
\newcommand{\job}[3]{%
  \underline{\textbf{#1}}, #2 \hfill #3\par\vspace{1pt}%
}

\newenvironment{jobitems}
  {\begin{itemize}[leftmargin=12pt,itemsep=1pt,parsep=0pt,topsep=1pt,label=\textbullet]}
  {\end{itemize}\vspace{5pt}}

% =====================================================================
\begin{document}

\begin{center}
  {\LARGE\bfseries M. Saqib Arfeen}\\[3pt]
  {\small\color{datedim}
    \href{mailto:saqib.arfeen@gmail.com}{saqib.arfeen@gmail.com} \,|\,
    \href{https://github.com/saqibarfeen}{github.com/saqibarfeen} \,|\,
    \href{https://www.linkedin.com/in/mohamedsaqib}{linkedin.com/in/mohamedsaqib}}
\end{center}
\vspace{6pt}

\cvsection{Summary}{%
Senior Software Engineer with 10 years of experience building backend systems,
distributed platforms, and cloud infrastructure --- including 3+ years shipping
product at a Berlin SaaS company. Strengths in high-availability system design,
performance troubleshooting, and taking products from architecture to production.}

\cvsection{Experience}{%
\job{Senior Software Engineer}{Ninox Software GmbH --- Berlin}{Nov '22 -- Feb '26}
\begin{jobitems}
  \item Designed and shipped core features of the Ninox low-code database
        platform (Node.js/TypeScript, React, Postgres), contributing to a
        sustained $\sim$20\% annual ARR growth.
  \item Scaled the platform and led performance investigations across the
        stack --- profiling, query optimization, and caching --- for a growing
        multi-tenant customer base.
  \item Worked directly with customer-facing teams to turn escalations into
        durable fixes and product improvements.
\end{jobitems}
\job{Senior Software Engineer}{Seed Labs --- Karachi}{Oct '21 -- Sep '22}
\begin{jobitems}
  \item Designed and implemented high availability for the in-memory order
        book of a low-latency decentralized exchange.
  \item Built backend components including the order-matching engine and
        blockchain settlement engine.
  \item Led migration to Kubernetes, significantly reducing fixed
        infrastructure costs while improving scalability.
\end{jobitems}
\job{Senior Software Engineer}{Folio3 Software --- Karachi}{Nov '19 -- Sep '21}
\begin{jobitems}
  \item Led development of ERP customizations and e-commerce integrations
        (NetSuite SuiteCloud, SuiteScript, React) for Fortune 500 clients.
  \item Created an internal knowledge base of ERP design patterns that
        measurably cut delivery time for routine projects.
\end{jobitems}
\job{Senior Software Engineer}{Ivolve Technologies --- Karachi}{Jul '19 -- Nov '19}
\begin{jobitems}
  \item Built hybrid-cloud middleware integrating OpenStack with public
        clouds; developed monitoring pipelines (Elasticsearch, Graphite,
        Grafana).
\end{jobitems}
\job{Software Engineer}{Cloud9 Networks FZE --- Dubai}{Jul '16 -- Jun '19}
\begin{jobitems}
  \item Architected and deployed a big-data analytics product (Hadoop, Hive,
        Java Spring) powering a customer-loyalty payment system in the MENA
        region.
  \item Built network/cloud monitoring systems covering thousands of customer
        premises devices, with alerting and ticketing integrations; helped win
        a contract with a top-tier Pakistani telecom.
  \item Trained and onboarded new developers into productive engineers.
\end{jobitems}}

\cvsection{Skills}{%
\textbf{Languages:} TypeScript/JavaScript, Java, Python, Go, C++\\
\textbf{Backend:} Node.js, NestJS, Spring, Flask; REST APIs, event-driven
systems (Kafka, RabbitMQ, Redis)\\
\textbf{Data:} Postgres, MySQL, MongoDB, Elasticsearch, InfluxDB, Hadoop/Hive,
Spark\\
\textbf{Cloud \& DevOps:} Kubernetes, AWS, OpenStack, Docker, GitHub Actions,
CircleCI, Prometheus, Grafana}

\cvsection{Education}{%
\job{BS Computer Science}{National University of Computer and Emerging
Sciences} {}
\begin{jobitems}
  \item Research Assistant (Machine Learning): deep learning on
        constraint-solver-generated puzzle data --- published in IJACSA 2017.
        Systems Engineer, Nvidia HPC Lab: built MPI and Hadoop clusters.
\end{jobitems}}

\cvsection{Languages}{English (fluent), German (A2)}

\end{document}
